It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-04-18 manuscript/manuscript.qmd
Add HTML
Add reference

Raw data and analysis-ready processed data is available as an R package
at @R-qechairquality. The data underlying the tables and figures of this
manuscript are contained in a repository alongside a reproducible
document that contains the analysis code and the written narrative of
the manuscript \[TODO: manuscript software citation\].

@@

percent_exposure |> 
  write_csv("data/processed-data/fig05-percent-exposure.csv")

>>>>

Raw data and analysis-ready processed data is available as an R package
at @R-qechairquality. The data underlying the tables and figures of this
manuscript are contained in a repository alongside a reproducible
document that contains the analysis code and the written narrative of
the manuscript [@schobitz2023manuscript].

@@

percent_exposure |> 
  write_csv(here::here("data/processed-data/fig05-percent-exposure.csv"))
